Approximation as Differentiation

### 2025-07-08 main/introduction.tex
Anonymise reference to GitHub repo.

We have \href{https://github.com/bobatkey/approx-diff}{formalised this work in Agda}. Not only does this mean that the constructions and proofs have been checked, but also the construction is executable and can be run on small examples. We are also planning to use Agda's JavaScript backend to produce a demo.% \todo{Do this?}

>>>>

We have \anonymise{\href{https://github.com/bobatkey/approx-diff}{formalised this work in Agda}}{formalised this work in Agda}. Not only does this mean that the constructions and proofs have been checked, but also the construction is executable and can be run on small examples. We are also planning to use Agda's JavaScript backend to produce a demo.
